%-------------------------
% Resume in LaTeX
% Based on Nicholas Russo's Pages resume layout
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage[margin=0.75in]{geometry}
\usepackage{fontspec}
\setmainfont{Inter}

% Page setup
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Spacing constants for uniformity
\newcommand{\sectionSpaceAbove}{-10pt}
\newcommand{\sectionSpaceBelow}{-4pt}
\newcommand{\afterListSpace}{-2pt}
\newcommand{\afterHeadingSpace}{-5pt}
\newcommand{\betweenItemsSpace}{-8pt}
\newcommand{\nestedListTopSpace}{3pt}

% Section formatting
\titleformat{\section}{
  \vspace{\sectionSpaceAbove}\scshape\raggedright\large\color{blue}
}{}{0em}{}[\color{blue}\titlerule \vspace{\sectionSpaceBelow}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{\afterHeadingSpace}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
      \small#1 & #2 \\
    \end{tabular*}\vspace{\afterHeadingSpace}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=\betweenItemsSpace]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{\afterListSpace}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, itemsep=0pt, topsep=\nestedListTopSpace]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{\afterListSpace}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Nicholas Russo} \\ \vspace{2pt}
    \small nijaru7@gmail.com $|$
    \href{https://github.com/nijaru}{github.com/nijaru} $|$
    \href{https://nijaru.com}{nijaru.com}
\end{center}
\vspace{-8pt}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Rust, Go, TypeScript, Ruby, C, C++} \\[2pt]
     \textbf{Backend/APIs}{: FastAPI, Flask, Django, Ruby on Rails, gRPC} \\[2pt]
     \textbf{Infrastructure}{: Docker, Linux (Fedora, Ubuntu, RHEL/CentOS, CoreOS, Gentoo), AWS, GCP, DigitalOcean, Cloudflare} \\[2pt]
     \textbf{Databases}{: PostgreSQL, SQLite, MySQL, Redis, ChromaDB, DuckDB} \\[2pt]
     \textbf{Tools}{: Git, GitHub Actions, PyO3, maturin, Bun, ONNX}
    }}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{omendb} $|$ \href{https://github.com/omendb/omendb}{\underline{github.com/omendb/omendb}} $|$ \emph{Rust, Python, TypeScript, PyO3, Vector Database}}{}
          \resumeItemListStart
            \resumeItem{Embedded vector database. 4x faster than hnswlib. Rust core with Python (PyO3/maturin) and TypeScript (napi-rs) bindings. Powers a Claude Code memory plugin for persistent agent context}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{ion} $|$ \href{https://github.com/nijaru/ion}{\underline{github.com/nijaru/ion}} $|$ \emph{Rust, AI/ML, TUI}}{}
          \resumeItemListStart
            \resumeItem{Multi-model coding agent TUI in Rust. Pluggable LLM backends with tool use and persistent context management across sessions}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{jb} $|$ \href{https://github.com/nijaru/jb}{\underline{github.com/nijaru/jb}} $|$ \emph{Rust, CLI}}{}
          \resumeItemListStart
            \resumeItem{Background job manager for long-running agent tasks. Tracks commands, streams logs, and persists state across sessions.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{tk} $|$ \href{https://github.com/nijaru/tk}{\underline{github.com/nijaru/tk}} $|$ \emph{TypeScript, Bun, CLI}}{}
          \resumeItemListStart
            \resumeItem{CLI task tracker for long-running agent workflows. Persists task state, logs, and progress to disk so multi-step work survives LLM context resets and session boundaries}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{omengrep} $|$ \href{https://github.com/nijaru/omengrep}{\underline{github.com/nijaru/omengrep}} $|$ \emph{Rust, Python, ONNX}}{}
          \resumeItemListStart
            \resumeItem{Semantic code search CLI. ONNX embeddings for concept-based retrieval and tree-sitter AST parsing for language-aware indexing across 22 languages}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{January 2021 - May 2023}
      {Omnitier, Inc.}{}
      \resumeItemListStart
        \resumeItem{Reduced test suite runtime by 90\% (45 min to 5 min) by profiling and reducing syscall overhead in filesystem operations}
        \resumeItem{Built gRPC Python API layer for distributed Go backend services}
        \resumeItem{Developed regression testing infrastructure across Go and Python codebases}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{2nd Place \& Ingenico Winner, Money 20/20 Las Vegas 2016} $|$ \emph{Team Kairos}}{}
          \resumeItemListStart
            \resumeItem{Developed cross-terminal payment application with REST API for business partnerships. Built with Go and PostgreSQL, deployed on CoreOS}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {42 Silicon Valley}{2018 - 2020}
      {Computer Science}{Fremont, CA}
    \resumeSubheading
      {Las Positas College}{2014 - 2015, 2016 - 2018}
      {Computer Science}{Livermore, CA}
      \resumeItemListStart
        \resumeItem{Computer Science Club President 2016 - 2017}
      \resumeItemListEnd
    \resumeSubheading
      {Dev Bootcamp}{March 2016 - May 2016}
      {Web Development}{San Francisco, CA}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
